MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-14 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
comment out nonessential code for testing

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Set annotations
all.annotations = list(
  dataType = 'geneExpression',
  dataSubtype = 'processed',
  assay	 = 'rnaSeq',

  tissue	= 'dorsolateral prefrontal cortex, anterior cingulate cortex', 
  study = 'CMC',

  species = 'Human',
  consortium	= 'CMC',

  analysisType	= "data normalization",

  transcriptNormalizationMethod	= 'CQN',
  transcriptQuantificationMethod = 'featureCounts',
  referenceSet = 'GRCh38'
)

# Code
CODE <- Folder(name = "test mvBIC - MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId)
CODE <- synStore(CODE)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = synapser::File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(COV_OBJ, annotations = all.annotations)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(COUNT_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
LCOUNT_OBJ = synStore(LCOUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(LCOUNT_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
OFFSET_OBJ = synStore(OFFSET_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(OFFSET_OBJ, annotations = all.annotations)
```

|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |

>>>>

<!-- ### Store files in synapse -->
<!-- ```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE} -->
<!-- # Set annotations -->
<!-- all.annotations = list( -->
<!--   dataType = 'geneExpression', -->
<!--   dataSubtype = 'processed', -->
<!--   assay	 = 'rnaSeq', -->

<!--   tissue	= 'dorsolateral prefrontal cortex, anterior cingulate cortex',  -->
<!--   study = 'CMC',  -->

<!--   species = 'Human', -->
<!--   consortium	= 'CMC', -->

<!--   analysisType	= "data normalization", -->

<!--   transcriptNormalizationMethod	= 'CQN', -->
<!--   transcriptQuantificationMethod = 'featureCounts', -->
<!--   referenceSet = 'GRCh38' -->
<!-- ) -->

<!-- # Code -->
<!-- CODE <- Folder(name = "test mvBIC - MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId) -->
<!-- CODE <- synStore(CODE) -->

<!-- # Store covariates -->
<!-- COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID') -->
<!-- write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F) -->
<!-- COV_OBJ = synapser::File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id) -->
<!-- COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName,  -->
<!--                       executed = thisFile, activityDescription = activityDescription) -->
<!-- synSetAnnotations(COV_OBJ, annotations = all.annotations) -->

<!-- # Store filtered counts -->
<!-- PROCESSED_COUNTS$filteredExprMatrix$counts %>% -->
<!--   rownameToFirstColumn('ensembl_gene_id') %>% -->
<!--   write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F) -->
<!-- COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id) -->
<!-- COUNT_OBJ = synStore(COUNT_OBJ, used = ALL_USED_IDs, activityName = activityName,  -->
<!--                       executed = thisFile, activityDescription = activityDescription) -->
<!-- synSetAnnotations(COUNT_OBJ, annotations = all.annotations) -->

<!-- # Store logCPM -->
<!-- CQN.GENE_EXPRESSION$E %>% -->
<!--   rownameToFirstColumn('ensembl_gene_id') %>% -->
<!--   write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F) -->
<!-- LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id) -->
<!-- LCOUNT_OBJ = synStore(LCOUNT_OBJ, used = ALL_USED_IDs, activityName = activityName,  -->
<!--                       executed = thisFile, activityDescription = activityDescription) -->
<!-- synSetAnnotations(LCOUNT_OBJ, annotations = all.annotations) -->

<!-- # Store cqn offsets -->
<!-- CQN.GENE_EXPRESSION$offset %>% -->
<!--   rownameToFirstColumn('ensembl_gene_id') %>% -->
<!--   write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F) -->
<!-- OFFSET_OBJ = File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id) -->
<!-- OFFSET_OBJ = synStore(OFFSET_OBJ, used = ALL_USED_IDs, activityName = activityName,  -->
<!--                       executed = thisFile, activityDescription = activityDescription) -->
<!-- synSetAnnotations(OFFSET_OBJ, annotations = all.annotations) -->
<!-- ``` -->

<!-- |  *Results*                                  |  *SynapseID*                     | -->
<!-- |  -----------------------------------------  |   ---------                      | -->
<!-- |  Covariates                                 |  `r COV_OBJ$properties$id`       | -->
<!-- |  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     | -->
<!-- |  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    | -->
<!-- |  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    | -->
